Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-27 review_article.Rmd
Small edits

<!-- what is a choropleth map -->
A choropleth map is used to display the characteristics of a spatial relationship of measurements. 
A choropleth map is a true map of the topology, constructed for visual inspection of spatial patterns on a familiar geographic form. 
\ref{fig:choro} 1 shows a choropleth map where each state of the United States of America is coloured by the average annual rate of new cases of lung and bronchus cancer from years 2012 to 2016.
Identifying and explaining spatial structures, patterns, and processes involves considering the individuals in communities and organising communities into representable units [@SAMGIS]. 
A choropleth is constructed by drawing the geographic or political boundaries, and filling the shapes with colours to represent values of a measured variable [@EI].
Early versions of choropleth maps used symbols or patterns instead of colour.
As an alternative storage device to a table, it preserves locations for geographically ordered data, with usage dating back to the 1800s [@GOINO].
@CPISACA discuss the use of choropleths to visualise cancer data, and @DMAHP gives an overview of the development of these maps for displaying disease data.

@@

>"designing a map tailored to precise goals [is] easier than forcing a single map to accommodate diverse objectives" @CPISACA

Waldo Tobler [-@TVSSS] explores many graphical techniques, and suggests there are particular methods for particular purposes. To choose an appropriate map display, the map creator must consider the intended user, and message the map will communicate.
Techonology has played an enormous role in increasing the opportunities for map makers.
The computation and graphics power have made creation, alteration and interactivity possible.
The internet has made communication of scientific data and results increasingly accessible.
Creating maps of dieases now involves more decisions as these options have expanded and it is the objectives of the investigator that will drive the choices. @CPISACA and @SAMGIS have provided suggestions and comments to help map creators best communicate their health data and spatial analyses.

>>>>

<!-- what is a choropleth map -->
A choropleth map is used to display the characteristics of a spatial relationship of measurements. 
They are true maps of the topology, constructed for visual inspection of spatial patterns on a familiar geographic form. Classed choropleth maps break a continuous variable into a small set of categories, often quintiles, and use a gradual colour scheme to shade all areas that fall in the same category [@CPISACA].
\ref{fig:choro} 1 shows a choropleth map where each state of the United States of America is coloured by the average annual rate of new cases of lung and bronchus cancer from years 2012 to 2016.
Identifying and explaining spatial structures, patterns, and processes involves considering the individuals in communities and organising communities into representable units [@SAMGIS]. 
A choropleth is constructed by drawing the geographic or political boundaries, and filling the shapes with colours to represent values of a measured variable [@EI].
Early versions of choropleth maps used symbols or patterns instead of colour.
As an alternative storage device to a table, it preserves locations for geographically ordered data, with usage dating back to the 1800s [@GOINO].
@CPISACA discuss the use of choropleths to visualise cancer data, and @DMAHP gives an overview of the development of these maps for displaying disease data.

@@

To choose an appropriate map display, the map creator must consider the intended user, and message the map will communicate.
To discover whether the display is appropriate, consider the  
Techonology has played an enormous role in increasing the opportunities for map makers.
The computation and graphics power have made creation, alteration and interactivity possible.
The internet has made communication of scientific data and results increasingly accessible.
Creating maps of dieases now involves more decisions as these options have expanded and it is the objectives of the investigator that will drive the choices. @CPISACA and @SAMGIS have provided suggestions and comments to help map creators best communicate their health data and spatial analyses.
